### 2017-02-23 Paper/Paper_Eric.tex
Added a first version of the introduction.

>>>>

In the following paper I will depart from the strong assumption of an exogenous job-finding probability, still using the baseline model. Based on the results of an empirical estimation of the relationship between changes in the unemployment rate and the job-finding probability I will let the latter fluctuate with the policy changes. I then show that this may completely change the outcome of the welfare analysis and therefore may have strong policy implications. It may not be sufficient to raise unemployment benefits without undertaking measures to reduce job-finding frictions, such as providing incentives and information to improve the transition from unemployment to employment.

I will start by discussing the model then go on by describing how I conducted the welfare analysis. In the thrid part I present my results after a brief summary of the results presented during our presentation - the baseline case with exogenous transition probabilities. Finally, I conclude with a critical discussion.
